The Lipid Interactome Repository

### 2025-03-31 IndividualStudies/DCC_2025.qmd
adding structures for NAPE and bf-NAPE

@@

## Opening the source file for the ggplot custom theme
source(paste0(here::here(), "/Resources/ggplot_styles.R"))

data <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
  group_by(gene_name) |>
  filter(ratio_MvsL != "") |>
  summarise(logFC = mean(log2(ratio_MvsL)),
            pvalue = mean(pvalue),
            numReplicates = n(),
            AveExpr = log10(mean(L_abundance) + mean(M_abundance))/2) |>
  arrange(-logFC) |>
  mutate(LipidProbe = "BF-NAPE",
         hit_annotation = case_when(.default = "no hit",
                                    logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 2 ~ "enriched candidate",
                                    logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 3 ~ "enriched hit")) |>
  glimpse()

median_logFC <- median(data$logFC)

data$logFC <- data$logFC - median_logFC

@@

# write_csv(data, paste0(here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_Download.csv"))

>>>>

```{r HiddenOriginalDataWrangling, include=FALSE, echo=FALSE}

# data <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
#   group_by(gene_name) |>
#   filter(ratio_MvsL != "") |>
#   summarise(logFC = mean(log2(ratio_MvsL)),
#             pvalue = mean(pvalue),
#             numReplicates = n(),
#             AveExpr = log10(mean(L_abundance) + mean(M_abundance))/2) |>
#   arrange(-logFC) |>
#   mutate(LipidProbe = "BF-NAPE",
#          hit_annotation = case_when(.default = "no hit",
#                                     logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 2 ~ "enriched candidate",
#                                     logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 3 ~ "enriched hit")) |>
#   glimpse()

# median_logFC <- median(data$logFC)

# data$logFC <- data$logFC - median_logFC

@@

## Opening the source file for the ggplot custom theme
source(here::here("Resources/ggplot_styles.R"))

data <- readr::read_csv(here::here("IndividualStudies/DataTables/DCC_2025_ChemrXiv_Download.csv"))

@@

# write_csv(data, here("IndividualStudies/DataTables/DCC_2025_ChemrXiv_Download.csv"))

### 2025-03-31 IndividualStudies/WY_2021.qmd
adding structures for NAPE and bf-NAPE

    MAPlots <- data |>
        ggplot(aes(x = AveExpr,
                   y = logFC,
                   color = factor(hit_annotation),
                   fill = factor(hit_annotation),
                   shape = factor(hit_annotation),
                   alpha = factor(hit_annotation),
                   size = factor(hit_annotation))) +
        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
                                    "LogFC: ", logFC, "\n",
                                    "AveExpr: ", AveExpr, "\n"))) +
        geom_hline(yintercept = 0, linetype = 2) +
        geom_vline(xintercept = 0, linetype = 2) +
        scale_x_continuous(limits = c(0.9 * min(abs(data$AveExpr)), 1.1 * max(abs(data$AveExpr))))+
        scale_y_continuous(limits = c(-1.1 * max(abs(data$logFC)), 1.1 * max(abs(data$logFC))))+
        scale_shape_manual(values = c("enriched hit" = 21,
                                    "hit" = 21,
                                    "enriched candidate" = 24,
                                    "candidate" = 24,
                                    "no hit" = 22), 
                        name = "Trend") +
        scale_color_manual(values = c("enriched hit" = "black",
                                    "hit" = "black",
                                    "enriched candidate" = "black",
                                    "candidate" = "black",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_fill_manual(values = c("enriched hit" = "orange",
                                    "hit" = "orange",
                                    "enriched candidate" = "purple",
                                    "candidate" = "purple",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_alpha_manual(values = c("enriched hit" = 0.8,
                                    "hit" = 0.8,
                                    "enriched candidate" = 0.5,
                                    "candidate" = 0.5,
                                    "no hit" = 0.25), 
                        name = "Trend") +
        scale_size_manual(values = c("enriched hit" = 4,
                                    "hit" = 4,
                                    "enriched candidate" = 2,
                                    "candidate" = 2, 
                                    "no hit" = 0.75), 
                        name = "Trend") +
        facet_wrap(~LipidProbe) +
        ylab("Log2 fold-change") +
        xlab("Average Ion Intensity") +
        theme_minimal() +
        theme(text = element_text(family = "serif")) +
        theme(panel.border = element_rect(color = NA, fill = NA)) +
        theme(legend.title = element_text(size = 12, face = "bold")) +
        theme(axis.title = element_text(size = 12, face = "bold")) +
        theme(legend.text = element_text(size = 12)) +
        theme(strip.text = element_text(
    size = 20))

@@

@@

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

RawData <- read_csv(paste0(here::here(), "/IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
  filter(Coverage != 0 & Fold_change != 0) |>
  mutate(gene_name = gene_name...3) |>
  group_by(gene_name) |>
  summarise(logFC = mean(log2(Fold_change)),
            # pvalue = mean(pvalue),
            numReplicates = n(),
            AveExpr = log10(mean(Control_abundance) + mean(Sample_abundance)/2)) |>
  arrange(-logFC)

median_logFC <- median(RawData$logFC)

RawData$logFC <- RawData$logFC - median_logFC

RawData <- RawData |> 
  mutate(LipidProbe = "PDAA",
        AveExpr = case_when(.default = AveExpr,
                              AveExpr == -Inf ~ 0),
                              hit_annotation = case_when(.default = "no hit",
                                                          logFC >= 0.5849625 & numReplicates == 2 ~ "enriched candidate",
                                                          logFC >= 0.5849625 & numReplicates == 3 ~ "enriched hit")) |>         
  glimpse()

nrow(RawData |> filter(hit_annotation == "enriched hit"))

# Organize the hit annotations as factors
RawData$hit_annotation <- factor(pull(RawData, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

# write_csv(RawData, paste0(here(), "/IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))

@@

RankedOrderPlotSpecial(RawData)
```

@@

MASpecial(RawData)
```

@@

VennData <- read_csv("DataTables/WY_2021_ACSChemBio_RawData.csv")  |>
  mutate(gene_name = Description)

@@

data <- RawData |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, numReplicates) |>
  mutate(logFC = signif(logFC, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation)

>>>>

    MAPlots <- data |>
        ggplot(aes(x = AveExpr,
                   y = logFC,
                   color = factor(hit_annotation),
                   fill = factor(hit_annotation),
                   shape = factor(hit_annotation),
                   alpha = factor(hit_annotation),
                   size = factor(hit_annotation))) +
        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
                                    "LogFC: ", logFC, "\n",
                                    "AveExpr: ", AveExpr, "\n"))) +
        geom_hline(yintercept = 0, linetype = 2) +
        geom_vline(xintercept = 0, linetype = 2) +
        scale_x_continuous(limits = c(0.9 * min(abs(data$AveExpr)), 1.1 * max(abs(data$AveExpr))))+
        scale_y_continuous(limits = c(-1.1 * max(abs(data$logFC)), 5))+
        scale_shape_manual(values = c("enriched hit" = 21,
                                    "hit" = 21,
                                    "enriched candidate" = 24,
                                    "candidate" = 24,
                                    "no hit" = 22), 
                        name = "Trend") +
        scale_color_manual(values = c("enriched hit" = "black",
                                    "hit" = "black",
                                    "enriched candidate" = "black",
                                    "candidate" = "black",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_fill_manual(values = c("enriched hit" = "orange",
                                    "hit" = "orange",
                                    "enriched candidate" = "purple",
                                    "candidate" = "purple",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_alpha_manual(values = c("enriched hit" = 0.8,
                                    "hit" = 0.8,
                                    "enriched candidate" = 0.5,
                                    "candidate" = 0.5,
                                    "no hit" = 0.25), 
                        name = "Trend") +
        scale_size_manual(values = c("enriched hit" = 4,
                                    "hit" = 4,
                                    "enriched candidate" = 2,
                                    "candidate" = 2, 
                                    "no hit" = 0.75), 
                        name = "Trend") +
        facet_wrap(~LipidProbe) +
        ylab("Log2 fold-change") +
        xlab("Average Ion Intensity") +
        theme_minimal() +
        theme(text = element_text(family = "serif")) +
        theme(panel.border = element_rect(color = NA, fill = NA)) +
        theme(legend.title = element_text(size = 12, face = "bold")) +
        theme(axis.title = element_text(size = 12, face = "bold")) +
        theme(legend.text = element_text(size = 12)) +
        theme(strip.text = element_text(
    size = 20))

@@

```{r HiddenDataWrangling, include=FALSE, echo=FALSE}

# RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
#   filter(Coverage != 0 & Fold_change != 0) |>
#   mutate(gene_name = gene_name...3) |>
#   group_by(gene_name) |>
#   summarise(logFC = mean(log2(Fold_change)),
#             # pvalue = mean(pvalue),
#             numReplicates = n(),
#             AveExpr = log10(mean(Control_abundance) + mean(Sample_abundance)/2)) |>
#   arrange(-logFC)

# median_logFC <- median(RawData$logFC)

# RawData$logFC <- RawData$logFC - median_logFC

# RawData <- RawData |> 
#   mutate(LipidProbe = "PDAA",
#         AveExpr = case_when(.default = AveExpr,
#                               AveExpr == -Inf ~ 0),
#                               hit_annotation = case_when(.default = "no hit",
#                                                           logFC >= 0.5849625 & numReplicates == 2 ~ "enriched candidate",
#                                                           logFC >= 0.5849625 & numReplicates == 3 ~ "enriched hit")) |>         
#   glimpse()

# write_csv(RawData, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))

@@

## Opening the source file for the ggplot custom theme
source(here("Resources/ggplot_styles.R"))

data <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

@@

RankedOrderPlotSpecial(data)
```

@@

MASpecial(data)
```

@@

VennData <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
  mutate(gene_name = gene_name...3)

@@

data <- data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, numReplicates) |>
  mutate(logFC = signif(logFC, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation)

### 2025-03-31 LipidProbe/N-Acylphosphatidylethanolamine.qmd
example
adding structures for NAPE and bf-NAPE

---
title: "Bifunctional N-Acylphosphatidylethanolamine"
subtitle: "NAPE"
prefer-html: true
format:
  html: default
callout-icon: false
---

@@

:::{.border}
::: {layout="[[-0.01,99.99], [100]]"}
<!-- ![(A) Native N-Acylphosphatidylethanolamine.](/LipidProbe/Structures/PE.png) -->

![(B) Bifunctional N-Acylphosphatidylethanolamine.](/LipidProbe/Structures/BF_NAPE.png)

@@

## Opening the source file for the ggplot custom theme
source(paste0(here::here(), "/Resources/ggplot_styles.R"))

data <- readr::read_csv(paste0(here::here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
  group_by(gene_name) |>
  filter(gene_name != "" & ratio_MvsL != "" & L_abundance != "" & M_abundance != "") |>
  summarise(logFC = mean(log2(ratio_MvsL)),
            pvalue = mean(pvalue),
            numReplicates = n(),
            AveExpr = log10(mean(mean(L_abundance), mean(M_abundance)))) |>
  arrange(logFC) |>
  mutate(LipidProbe = "BF-NAPE",
         hit_annotation = case_when(.default = "no hit",
                                    logFC >= 0.5849625 & pvalue <= 0.01 & numReplicates == 2 ~ "enriched candidate",
                                    logFC >= 0.5849625 & pvalue <= 0.01 & numReplicates == 3 ~ "enriched hit")) |>
  glimpse()

median_logFC <- median(data$logFC)

data$logFC <- data$logFC - median_logFC

@@

```{r save_csv, include=FALSE, echo=FALSE, warning=FALSE}

# write_csv(data, paste0(here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_Download.csv"))

>>>>

---
title: "Bifunctional N-Acylphosphatidylethanolamine"
subtitle: "NAPE"
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@

:::{.border}
::: {layout="[[-0.01,99.99], [100]]"}
![(A) Native N-Acylphosphatidylethanolamine.](/LipidProbe/Structures/NAPE.png)

![(B) Bifunctional N-Acylphosphatidylethanolamine.](/LipidProbe/Structures/BF-NAPE.png)

@@

## Opening the source file for the ggplot custom theme
source(here::here("Resources/ggplot_styles.R"))

data <- readr::read_csv(here::here("LipidProbe/DataSets/DCC_2025_ChemrXiv_Download.csv"))

@@

### 2025-03-31 StudyInformation_includes/DH_2017_include.qmd
adding structures for NAPE and bf-NAPE

[Trifunctional Sphingosine](/LipidProbe/Sphingosine.qmd)

[Trifunctional Diacylglycerol](/LipidProbe/Diacylglycerol.qmd)

[Trifunctional 8-3 Fatty acid](/LipidProbe/8-3_FattyAcid.qmd)

>>>>

<a href="/LipidProbe/Sphingosine.qmd" class="hover-preview">Trifunctional Sphingosine</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_Sphingosine.png" alt="Trifunctional Sphingosine" />
</span>

<a href="/LipidProbe/Diacylglycerol.qmd" class="hover-preview">Trifunctional Diacylglycerol</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_DAG.png" alt="Trifunctional Diacylglycerol" />
</span>

<a href="/LipidProbe/8-3_FattyAcid.qmd" class="hover-preview">Trifunctional 8-3 Fatty Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_8-3_fatty_acid.png" alt="Trifunctional 8-3 Fatty Acid" />
</span>
